---
title: "spitzemap_construction"
author: "Chris Mathy"
email: "chris.mathy@ucsf.edu"
date: "3/22/2019"
output: html_document
---

import packages
```{r echo=T, results='hide'}
library(tidyverse)
```

Read in the Gsp1 data, output from MATLAB
- The data is processed to have six labels for each strain (query or array) to match the labels
  used for the SGA preprocessing.
```{r}
name_to_ORF <- list()
name_to_ORF$array_allele_name <- read_delim('gsp1_pEMAP_avg_merged_gene_names.txt', delim='\t') %>% colnames()
name_to_ORF$array_ORF <- read_delim('gsp1_pEMAP_avg_merged.txt', delim='\t') %>% colnames()
name_to_ORF <- as.data.frame(name_to_ORF)

gsp1_pEMAP <-
  read_delim('gsp1_pEMAP_avg_merged_gene_names.txt', delim='\t') %>% 
  rename(query_allele_name = Gene) %>%
  separate(query_allele_name, into = c('query_name', 'query_mutant'),
           sep = ' - ', extra = "drop", remove = FALSE) %>% 
  mutate(query_ORF = 'YLR293C', query_descriptor = NA) %>% 
  unite('query_strain_id', c('query_ORF','query_mutant'), remove = FALSE) %>% 
  gather(-starts_with('query'), key = 'array_allele_name', value = 'score', na.rm = TRUE) %>%
  left_join(name_to_ORF, by = 'array_allele_name') %>% 
  separate(array_allele_name, into = c('array_name', 'array_descriptor'),
           sep = ' - ', extra = "drop", remove = FALSE) %>% 
  mutate('array_mutant' = NA,
         'array_strain_id' = paste(array_ORF, 'emap', sep = '_'),
         'interaction_network' = 'gsp1_pEMAP',
         'pvalue' = NA) %>%
  select(starts_with('query'), starts_with('array'), score, pvalue, interaction_network)
```

import SGA data and prepare it for concatenation
```{r}
load('../scaling_Costanzo_SGA_data/data/SGA_2016_full_scaled.rda')

SGA_to_combine <-
  SGA_scaled_to_EMAP %>% 
  mutate(interaction_network = paste(interaction_network, 'SGA', sep = '_')) %>% 
  select(interaction_network, starts_with('query'), starts_with('array'),
         -ends_with('smf'), -arraytype_temp, score_scaled_to_emap, pvalue) %>% 
  rename('score' = score_scaled_to_emap)
```

Combine pEMAP with SGA to make spitzemap, then save
```{r}
spitzemap <- bind_rows(gsp1_pEMAP, SGA_to_combine)
save(spitzemap, file = 'spitzemap.rda')
```

Prepare the "spitzemapko", which only includes KOs as arrays, for use in
computing correlatons to Gsp1 mutant profiles.
```{r}
spitzemapko <-
  spitzemap %>% 
  filter(interaction_network %in% c('gsp1_pEMAP','ExN_SGA','NxN_SGA'),
         !grepl('supp', query_allele_name), # exclude strains with suppressive mutations
         !grepl('supp', array_allele_name),
         !grepl('_tsa', array_strain_id)) # exclude ts array genes (not in gsp1 emap library anyway)

save(spitzemapko, file = 'spitzemapko.rda')
```

Show that all arrays are deletions (SGA from dma, or from gsp1 emap, which has only deletions)
```{r}
spitzemapko %>%
  filter(!grepl('dma', array_strain_id),
         !grepl('emap', array_strain_id))
```

Find the intersecting array ORFs between the SGA and Gsp1 EMAP
```{r}
# find intersecting arrays between the Gsp1 EMAP and the SGA
gsp1_arrays <- 
  spitzemapko %>% 
  filter(interaction_network == 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% 
  distinct() %>% 
  unlist()

sga_arrays <-
  spitzemapko %>% 
  filter(interaction_network != 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% 
  distinct() %>% 
  unlist()

shared_arrays <- intersect(gsp1_arrays, sga_arrays)

print(length(gsp1_arrays))
print(length(sga_arrays))
print(length(shared_arrays))

# [1] 1444
# [1] 3827
# [1] 1137
```

We must use unique id's whenever spreading, otherwise there
will be multiple values for the same row-column pair in the
wide format matrix. The following code shows that when using
the strain_id's as unique id's, the number of distinct rows
is equal to the number of rows of spitzemap_for_corr.
```{r}
spitzemapko %>% 
  select(query_strain_id, array_ORF, score) %>%
  distinct() %>% 
  nrow() %>% 
  print()
print(nrow(spitzemapko))
# [1] 14375673
# [1] 14375673
```

The following full spreading (long => wide) works for the full matrix,
so the unique id's work. Note that this takes a while to run (5min)
```{r}
cormat <-
  spitzemapko %>% 
  select(query_strain_id, array_ORF, score) %>%
  spread(query_strain_id, score) %>% 
  select(-array_ORF) %>% 
  cor(., use = "pairwise.complete.obs", method = 'pearson')
```


As an example case, the following code runs correlations for all of the Gsp1
partners that are included in the SGA as queries as well as all of the Gsp1
point mutants from our EMAP. We only use library/array genes that overlap
between the two datasets.
```{r}
library(factoextra)
library(reshape2)

load('spitzemapko.rda')
partners <- read_delim('partners.txt', delim = ',')

# find intersecting arrays between the Gsp1 EMAP and the SGA
gsp1_arrays <- filter(spitzemapko, interaction_network == 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% distinct() %>% unlist()
sga_arrays <- filter(spitzemapko, interaction_network != 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% distinct() %>% unlist()
shared_arrays <- intersect(gsp1_arrays, sga_arrays)

cormat <-
  spitzemapko %>% 
  filter(query_ORF %in% partners$ORF) %>%
  filter(array_ORF %in% shared_arrays) %>% 
  select(query_strain_id, array_ORF, score) %>% 
  spread(query_strain_id, score) %>% 
  select(-array_ORF) %>% 
  cor(., use = "pairwise.complete.obs", method = 'pearson')

new_names <-
  spitzemapko %>% 
  filter(query_ORF %in% partners$ORF) %>%
  select(query_strain_id, query_allele_name) %>%
  distinct() %>% 
  slice(match(colnames(cormat), query_strain_id)) %>% 
  select(query_allele_name) %>% 
  unlist()

colnames(cormat) <- new_names
rownames(cormat) <- new_names

dd <- as.dist((1-cormat)/2) # create a distance matrix, corr of "1" has dist 0 and "-1" has dist 1
hc <- hclust(dd) 
fviz_dend(hc, k = 6)
ggsave('dend.png', height = 10, width = 20)

cormat2 <- cormat[hc$order, hc$order]
melted_cormat2 <- melt(cormat2)
ggplot(data = melted_cormat2, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1),
                       low = "blue",
                       mid = "white",
                       high = "red") + 
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle = 90, hjust = 1))
ggsave('heatmap.png', height = 20, width = 20)

```


