---
title: "spitzemapko_partner_corr"
author: "Chris Mathy"
date: "3/22/2019"
output: html_document
---

load packages, data
```{r}
library(tidyverse)
library(factoextra)
library(reshape2)
library(psych)

load('spitzemapko.rda')
partners <- read_delim('partners.txt', delim = ',')
```

As an example case, the following code runs correlations for all of the Gsp1
partners that are included in the SGA as queries as well as all of the Gsp1
point mutants from our EMAP. We only use library/array genes that overlap
between the two datasets.
```{r}
# find intersecting arrays between the Gsp1 EMAP and the SGA
gsp1_arrays <- filter(spitzemapko, interaction_network == 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% distinct() %>% unlist()
sga_arrays <- filter(spitzemapko, interaction_network != 'gsp1_pEMAP') %>% 
  select(array_ORF) %>% distinct() %>% unlist()
shared_arrays <- intersect(gsp1_arrays, sga_arrays)
```

Using the corr.test function from the 'psych' package, compute pearson
correlations and 
```{r}
cormat <-
  spitzemapko %>% 
  filter(query_ORF %in% partners$ORF) %>%
  filter(array_ORF %in% shared_arrays) %>% 
  # mutate('score' = case_when(abs(score) < 2 ~ 0,
  #                            TRUE ~ score)) %>% # option to add a score threshold
  select(query_strain_id, array_ORF, score) %>% 
  spread(query_strain_id, score) %>% 
  select(-array_ORF) %>% 
  corr.test(., use = "pairwise.complete.obs", method = 'pearson', adjust = 'none')
```

Create a mask based on p-values, such that we ony consider correlations with
p-values < 0.05. Then apply the mask to the correlation matrix.
```{r}

mask <- cormat$p
mask[mask >= 0.05] = NA 
mask[mask < 0.05] = 1
mask[is.na(mask)] = 0
mask

cormat <- mask * cormat$r
cormat[is.na(cormat)] = 0

new_names <-
  spitzemapko %>% 
  filter(query_ORF %in% partners$ORF) %>%
  select(query_strain_id, query_allele_name) %>%
  distinct() %>% 
  slice(match(colnames(cormat), query_strain_id)) %>% 
  select(query_allele_name) %>% 
  unlist()

colnames(cormat) <- new_names
rownames(cormat) <- new_names

dd <- as.dist((1-cormat)/2) # create a distance matrix, corr of "1" has dist 0 and "-1" has dist 1
hc <- hclust(dd) 
fviz_dend(hc, k = 6)
ggsave('dend_p_filtered.png', height = 10, width = 20)

cormat2 <- cormat[hc$order, hc$order]
melted_cormat2 <- melt(cormat2)
ggplot(data = melted_cormat2, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() + 
  scale_fill_gradient2(limits = c(-1, 1),
                       low = "blue",
                       mid = "white",
                       high = "red") + 
  theme(text = element_text(size=20),
        axis.text.x = element_text(angle = 90, hjust = 1))
ggsave('heatmap_p_filtered.png', height = 20, width = 20)

```
