---CJM, Tuesday Mar 5, 2019---
Realized that the datasets output by the computeAveragedScores_hannes4
script are ready to be used by Colm's scaling, so no pre-processing
is necessary for the EMAP data. Here's how I was preprocessing it, but
honestly it's probably not useful anymore, because as long as I have
the SGA symmetric data prepared in a way that allows for Colm's script
to identify overlapping interactions (i.e., as long as the ORFs that 
need to be compared are identical), the cF3 needs no pre-processing.
This works because the DAmP, pseudogene, and ts gene names are always
ORF - DAMP or ORF - delta ybrxxx, and I don't name my SGA variables
like that.

I prep an SGA dataset using unique IDs that allow for marker swaps
to be averaged, but ultimately only the subset NxN with KOs will
be used for the averaging to the cF3. These will just use ORF as
gene names, meaning no pre-processing is needed for cF3.


--

Define a function to read and process E-MAP screens in the Krogan Lab file format
- Note that all of the data files here encode square matrices, where the rows in "Gene" are the same
  order as the columns after "Gene"
- Additionally, the datafiles for processing ORFs will have ORFs in the form "ORF - ORF" for knockdown strains
  (as opposed to "ORF" for knockout strains), and the string is always the same before and after the hyphen. For
  this reason, geneA_ID is dropped after separating out the ORF ID into geneA_name and geneA_perturbation.
```{r}
parse_emap <- function(dataset) {
  
  data <-
    read_delim(paste0('data/krogan_lab_EMAP_screens/', dataset, '_gene_names.txt'), delim='\t') %>% 
    rename(geneA_strain = Gene) %>% 
    mutate(geneA_ID = read_delim(paste0('data/krogan_lab_EMAP_screens/', dataset, '.txt'), delim='\t')$Gene) %>%
    select(geneA_ID, geneA_strain, everything()) %>% 
    separate(geneA_ID, into = c('geneA_ORF'), sep =' - ', extra = "drop", remove = TRUE) %>%
    separate(geneA_strain, into = c('geneA_name','geneA_perturbation'), sep =' - ', remove = FALSE) %>%
    mutate(geneA_perturbation = ifelse(is.na(geneA_perturbation), "KO", geneA_perturbation))
  
  strain_info <- 
    data %>% 
    select(starts_with('geneA')) %>% 
    rename(geneB_ORF = geneA_ORF,
           geneB_strain = geneA_strain,
           geneB_name = geneA_name,
           geneB_perturbation = geneA_perturbation)
  
  data %>%
    gather(-starts_with('geneA'), key = 'geneB_strain', value = 'score', na.rm = TRUE) %>% 
    left_join(strain_info, by = c('geneB_strain' = 'geneB_strain')) %>% 
    mutate(dataset = dataset) %>% 
    select(dataset, starts_with('geneA'), starts_with('geneB'), score)
}
```


Read in EMAP data, then column-wise concatenate, and save files
```{r}
TF <- parse_emap('TF')                     # TF, transcription factor emap [not 1536]
cF3 <- parse_emap('cF3')                   # cF3, chromosome biology emap [not 1536]
combRNAP <- parse_emap('combRNAP')         # combRNAP, RNA processing [not 1536]
cc2I <- parse_emap('cc2I')                 # cc2I, cell cycle screens (unpublished?)
endo <- parse_emap('endo')                 # endo, endocytosis emap (unpublished?) [not 1536]
espT <- parse_emap('espT')                 # espT, early secretory pathway emap [not 1536]
kinase <- parse_emap('kinase')             # kinase, kinase emap [not 1536]
scorematQC1p <- parse_emap('scorematQC1p') # scorematQC1p, lipid emap [1536]
slp <- parse_emap('slp')                   # slp, mitochondrial emap [1536]

# bind emap data together
EMAP <- bind_rows(TF, cF3, combRNAP, cc2I, endo, espT, kinase, scorematQC1p, slp)

# write datafiles
# Rdata
save(EMAP, file='data/EMAP_full.rda') 

# Tab-delimited text
# write_delim(EMAP, 'data/EMAP_full.txt', delim = '\t')
```


- For the EMAP, only the cF3 (chromosome biology) dataset is used, as this was the dataset
  chosen as reference in the original EMAP scaling paper (Ryan et al 2012 Molecular Cell),
  and other EMAPs have been scaled to it previously.
- Within the cF3, only KO perturbations are considered. The other perturbations include DAmPs,
  pseudogene deletions, and four point mutant temperature sensitive strains. Non-KO perturbations
  were excluded because DAmPs were excluded from the preprocessed SGA dataset and because there
  are relatively few pseudogene and ts mutant measurements.
  
  The following code shows that:
    - The dataset includes 305164 interactions
    - KO x KO measurements make up 80.8% of the dataset (n_interactions = 246502)
    - measurements involving a DAmP make up 48152/305164 = 15.8% of the dataset
    - measurements involving at least one pseudogene or ts mutant make up only 3.8% of the
      dataset (n = 11582)

```{r}
filter(EMAP, dataset == 'cF3') %>% summarise(n())
filter(EMAP, dataset == 'cF3') %>% filter((geneA_perturbation == 'KO') & (geneB_perturbation == 'KO')) %>% summarise(n())
filter(EMAP, dataset == 'cF3') %>% filter((geneA_perturbation == 'DAMP') | (geneB_perturbation == 'DAMP')) %>% summarise(n())
filter(EMAP, dataset == 'cF3') %>%
  filter( !(geneA_perturbation %in% c('KO','DAMP')) | !(geneB_perturbation %in% c('KO','DAMP'))) %>%
  summarise(n())
```


Once the cF3 data is filtered to only include KO x KO measurements, it can be confirmed that
  query_ORF == query_strain == query_name, so query_ORF can be renamed "query_unique_id" and the
  others can be dropped. The same is true for the array ORFs.

```{r}
EMAP_cF3_KOs <- EMAP %>%
  filter(dataset == 'cF3') %>% 
  filter((geneA_perturbation == 'KO') & (geneB_perturbation == 'KO')) %>% 
  select(geneA_ORF, geneB_ORF, score)
```

- Note that the EMAP long format was generated from a square matrix because it was already
  averaged/pseudo-averaged using the EMAP toolbox. This resulted in duplicate gene pairs with
  the same score (i.e. score(geneA, geneB) = score(geneB, geneA)) being reported twice in our
  table. This is shown in the following code, which sorts the query_unique_id and the
  array_unique_id alphabetically, groups by genes and score, and identifies that all gene
  pair - score combinations are replicated twice.
- To resolve this, simply call "distinct" after grouping by Pert1, Pert2, score)
  
```{r}
# Identify AB vs BA duplicates
EMAP_cF3_KOs %>% 
  rowwise() %>%
  mutate(geneA = min(geneA_ORF, geneB_ORF), geneB = max(geneA_ORF, geneB_ORF)) %>%
  ungroup() %>% 
  group_by(geneA, geneB, score) %>%
  mutate(n_rep = n()) %>% 
  ungroup() %>% 
  group_by(n_rep) %>% 
  summarise(n())

# Remove AB vs BA duplicates
EMAP_for_scaling <-
  EMAP_cF3_KOs %>% 
  rowwise() %>%
  mutate(geneA = min(geneA_ORF, geneB_ORF), geneB = max(geneA_ORF, geneB_ORF)) %>%
  ungroup() %>% 
  select(geneA, geneB, score) %>% 
  distinct() %>% 
  ungroup()

# Check that removal was successful
EMAP_for_scaling %>% 
  group_by(geneA, geneB) %>% 
  mutate(n_rep = n()) %>% 
  ungroup() %>% 
  group_by(n_rep) %>%
  summarise(n())

```

This table "EMAP_for_scaling" is now ready to be made into a square, symmetric format and used for scaling.
```{r}
write_delim(EMAP_for_scaling, 'data/EMAP_for_scaling_long.txt', delim = '\t')
```



Now, run the python script "sga_emap_long_to_symm.py", which converts the long form table into a symmetric
matrix using pandas dataframes.