---
title: "Parsing and organizing Wodak yest complexes"
output: html_notebook
---
```{r}
#### parse the Wodak yeast complexes in order to use them as clusters for the correlation calculations
wodak_data <- read.delim("CYC2008_complex.tab.txt", head = T)
wodak_data <- wodak_data[,c(1,3,2)]
head(wodak_data)
```
```{r}
length(wodak_data[,1])
```

```{r}
length( unique(wodak_data$Complex) )
```


```{r}
#### remove all the complexes that have 4 or fewer members (they will most likely give noisy correlations/dot products)
complex_member_count <- with(wodak_data, aggregate(Name, by = list(Complex = Complex), length))
complexes_to_keep <- complex_member_count[ complex_member_count[["x"]] > 6, ][["Complex"]]
length(complexes_to_keep)
```
```{r}
wodak_data <- wodak_data[ wodak_data$Complex %in% complexes_to_keep, ]
length(wodak_data[,1])
```
```{r}
names(wodak_data) <- c("ORF", "cluster", "gene_name")
head(wodak_data)
```

```{r}
write.table(file = "wodak_complex.txt", wodak_data, quote = F, row.names = F, sep="\t")
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

