
```{r, include=FALSE}
library(tidyverse)  # data manipulation
library(gplots)
library(gridGraphics)
library(grid)
library(gridExtra)
library(RColorBrewer)
# library(cluster)    # clustering algorithms
# library(factoextra) # clustering visualization
# library(dendextend) # for comparing two dendrograms
set.seed(94158)
```

```{r}
# prepare list of mutant orderings for displaying heatmaps in different row orders
mut_orderings <- list()
mut_orderings$seq_order <- scan('gsp1_mutants_ordered_by_residue.txt',
                                what="", sep="\n", quiet=TRUE)

# get list of mutants for which we have GAP and GEF data
mutants_with_GAP_GEF_data <- read_delim('datasets/GAP_GEF_ratio_for_clustering.txt',
                                        delim = '\t', col_types = cols())$mutant

# define clustering function
clustfn <- function(mat) {
  cormat <- cor(mat, use = "pairwise.complete.obs", method = "pearson")
  dissim <- as.dist((1 - cormat)/2)
  hc <- hclust(dissim, method = "average" )
  return(hc)
}
```

cluster full emap
```{r}
# Read in full emap for clustering
dset <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols())

# cluster mutants
mut.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
colnames(mut.mat) <- dset %>% pull(mutant)
mut.hc <- clustfn(mut.mat)

# save mutant orderings
ordering <- mut.hc$labels[mut.hc$order]
mut_orderings$full_emap <- ordering
mut_orderings$full_emap_GAPGEF_cluster_then_filter <- ordering[ordering %in% mutants_with_GAP_GEF_data]

# cluster arrays
arr.mat <- select(dset, -mutant) %>% as.matrix()
rownames(arr.mat) <- dset %>% pull(mutant)
arr.hc <- clustfn(arr.mat)

# make a heatmap of the full emap, with mutants and arrays clustered
pdf('images/gsp1_emap_full.pdf', height = 10, width = 60)
heatmap.2(arr.mat,
          Rowv = as.dendrogram(mut.hc), Colv = as.dendrogram(arr.hc),
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101),
          trace='none', density.info="none",
          lhei = c(1.5, 6), lwid = c(0.25, 6),
          cexCol = 0.3, cexRow = 1)
dev.off()

# also plot emap without mutant clustering (previously ordered by residue)
pdf('images/gsp1_emap_full_mutants_ordered_by_res.pdf', height = 10, width = 60)
heatmap.2(arr.mat,
          Rowv = FALSE, Colv = as.dendrogram(arr.hc), dendrogram = 'column',
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101),
          trace='none', density.info="none",
          lhei = c(1.5, 6), lwid = c(0.25, 6),
          cexCol = 0.3, cexRow = 1)
dev.off()

# store trees in better described objects
full_emap <- list()
full_emap$mut.mat <- mut.mat
full_emap$arr.mat <- arr.mat
full_emap$row.tree <- mut.hc
full_emap$col.tree <- arr.hc

```

cluster full emap, GAPGEF only
```{r}
# Read in full emap for clustering
dset <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols()) %>% 
  filter(mutant %in% mutants_with_GAP_GEF_data)

# cluster mutants
mut.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
colnames(mut.mat) <- dset %>% pull(mutant)
mut.hc <- clustfn(mut.mat)

# save mutant orderings
ordering <- mut.hc$labels[mut.hc$order]
mut_orderings$full_emap_GAPGEF_filter_then_cluster <- ordering

# cluster arrays
arr.mat <- select(dset, -mutant) %>% as.matrix()
rownames(arr.mat) <- dset %>% pull(mutant)

# filtering for GAP/GEF completeness leaves 3 pairs of array gene
# correlations as NA, so replace these with maximum distance values (1.0)
cormat <- cor(arr.mat, use = "pairwise.complete.obs", method = "pearson")
dissim <- as.dist((1 - cormat)/2)
dissim[which(sapply(dissim, function(x)all(is.na(x))))] <- 1.0
arr.hc <- hclust(dissim, method = "average" )

# make a heatmap of the full emap, with mutants and arrays clustered
pdf('images/gsp1_emap_full_GAPGEF_only.pdf', height = 10, width = 60)
heatmap.2(arr.mat,
          Rowv = as.dendrogram(mut.hc), Colv = as.dendrogram(arr.hc),
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101),
          trace='none', density.info="none",
          lhei = c(1.5, 6), lwid = c(0.25, 6),
          cexCol = 0.3, cexRow = 1)
dev.off()

# also plot emap without mutant clustering (previously ordered by residue)
pdf('images/gsp1_emap_full_GAPGEF_only_mutants_ordered_by_res.pdf', height = 10, width = 60)
heatmap.2(arr.mat,
          Rowv = FALSE, Colv = as.dendrogram(arr.hc), dendrogram = 'column',
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101),
          trace='none', density.info="none",
          lhei = c(1.5, 6), lwid = c(0.25, 6),
          cexCol = 0.3, cexRow = 1)
dev.off()

# store trees in better described objects
full_emap_GAP_GEF_mutmat <- mut.mat
full_emap_GAP_GEF_arrmat <- arr.mat
full_emap_GAP_GEF_rowtree <- mut.hc
full_emap_GAP_GEF_coltree <- arr.hc
```

cluster interface dataset
```{r}
# Read in full emap for clustering
dset <- read_delim('datasets/core_deltarASA_by_mutant_for_clustering.txt', delim = '\t', col_types = cols())

# cluster mutants
mut.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
colnames(mut.mat) <- dset %>% pull(mutant)
cormat <- cor(mut.mat, use = "everything", method = "pearson")
cormat[1:3,] = 1
cormat[,1:3] = 1
dissim <- as.dist((1 - cormat)/2)
mut.hc <- hclust(dissim, method = "average" )

# save mutant orderings
ordering <- mut.hc$labels[mut.hc$order]
mut_orderings$interface <- ordering
mut_orderings$interface_GAPGEF_cluster_then_filter <- ordering[ordering %in% mutants_with_GAP_GEF_data]

# cluster arrays
partner <- list()
partner.mat <- select(dset, -mutant) %>% as.matrix()
rownames(partner.mat) <- dset %>% pull(mutant)
partner.hc <- clustfn(partner.mat)

# heatmap
pdf('images/interface_clustering.pdf', height = 10, width = 8)
heatmap.2(partner.mat,
          Rowv = as.dendrogram(mut.hc), Colv = as.dendrogram(partner.hc),
          breaks = seq(0, 1, length.out = 101),
          col = colorRampPalette(c("black","cyan")),
          trace='none', density.info="none",
          main = 'Clustered by change in ASA after binding partner',
          lmat = rbind(c(0,3,0),c(2,1,0),c(0,4,0)),
          lhei = c(0.5,4,0.75), lwid = c(0.5,4,0.25),
          cexCol = 1.5, cexRow = 1.25, srtCol=45)
dev.off()

# store trees in better described objects
interface_mutmat <- mut.mat
interface_arrmat <- partner.mat
interface_rowtree <- mut.hc
interface_coltree <- partner.hc
```

cluster interface dataset, GAPGEF only
```{r}

# Read in full emap for clustering
dset <- read_delim('datasets/core_deltarASA_by_mutant_for_clustering.txt', delim = '\t', col_types = cols()) %>% 
  filter(mutant %in% mutants_with_GAP_GEF_data)

# cluster mutants
mut.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
colnames(mut.mat) <- dset %>% pull(mutant)
cormat <- cor(mut.mat, use = "everything", method = "pearson")
cormat[1:3,] = 1
cormat[,1:3] = 1
dissim <- as.dist((1 - cormat)/2)
mut.hc <- hclust(dissim, method = "average" )

# save mutant orderings
ordering <- mut.hc$labels[mut.hc$order]
mut_orderings$interface_GAPGEF_filter_then_cluster <- ordering

# cluster arrays
partner <- list()
partner.mat <- select(dset, -mutant) %>% as.matrix()
rownames(partner.mat) <- dset %>% pull(mutant)
partner.hc <- clustfn(partner.mat)

# heatmap
pdf('images/interface_GAPGEF_only_clustering.pdf', height = 10, width = 8)
heatmap.2(partner.mat,
          Rowv = as.dendrogram(mut.hc), Colv = as.dendrogram(partner.hc),
          breaks = seq(0, 1, length.out = 101),
          col = colorRampPalette(c("black","cyan")),
          trace='none', density.info="none",
          main = 'Clustered by change in ASA after binding partner',
          lmat = rbind(c(0,3,0),c(2,1,0),c(0,4,0)),
          lhei = c(0.5,4,0.75), lwid = c(0.5,4,0.25),
          cexCol = 1.5, cexRow = 1.25, srtCol=45)
dev.off()

# store trees in better described objects
interface_GAP_GEF_mutmat <- mut.mat
interface_GAP_GEF_arrmat <- partner.mat
interface_GAP_GEF_rowtree <- mut.hc
interface_GAP_GEF_coltree <- partner.hc
```

cluster GAP/GEF dataset
```{r}
# Read in full emap for clustering
dset <- read_delim('datasets/GAP_GEF_effic_for_clustering.txt', delim = '\t', col_types = cols())

# cluster mutants
mut.mat <- select(dset, -mutant) %>% as.matrix()
rownames(mut.mat) <- dset %>% pull(mutant)
distmat <- dist(mut.mat, method = "euclidean")
mut.hc <- hclust(distmat, method = "average")

mut_orderings$GAPGEF_effic <- mut.hc$labels[mut.hc$order]

# make a heatmap of the full emap, with mutants and arrays clustered
pdf('images/GAPGEF_clustering.pdf', height = 10, width = 6)
heatmap.2(mut.mat,
          Rowv = as.dendrogram(mut.hc), Colv = FALSE, dendrogram = 'row',
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101),
          trace='none', density.info="none",
          lmat = rbind(c(0,3,0),c(2,1,0),c(0,4,0)),
          lhei = c(0.5,4,1), lwid = c(0.5,2,0.25),
          cexCol = 1, cexRow = 1, srtCol=0, adjCol = 0.5)
dev.off()

GAP_GEF_mutmat <- mut.mat
GAP_GEF_rowtree <- mut.hc

```

Cut EMAP into k clusters, and consider only those clusters with at least 3
members. After examining the SGD descriptions, about half (21/44) strongly
enrich one biological process or complex. These clusters were manually labeled
and the file 'subset_cluster_names.txt' was made.
NOTE: different clusters if you filter to GAP/GEF complete first
```{r}
# set k = number of clusters to make
k = 1200
cluster_assignements <- cutree(full_emap_coltree, k = k)
# cluster_assignements <- cutree(full_emap_GAP_GEF_coltree, k = k)
clusters_with_descriptions <-
  data.frame('name' = names(cluster_assignements),
             'cluster_number' = unname(cluster_assignements),
             stringsAsFactors = FALSE) %>% 
  left_join(read_delim('SGD_descriptions.txt', delim='\t', col_types = cols()), by = 'name')

clusters_with_descriptions %>% 
  write_delim('unbiased_array_clusters_with_descriptions.txt', delim='\t')

cluster_dir = 'clusters/'
dir.create(file.path(getwd(), cluster_dir))

written <- clusters_with_descriptions %>% 
           group_by(cluster_number) %>% 
           filter(n() > 2) %>% 
           nest(.key = 'cluster_data') %>% 
           mutate(data = walk2(cluster_data,
                               paste0(cluster_dir, '/', cluster_number, '.csv'),
                               delim = ',', na = '', write_delim))
```

Make gene sets
```{r}

gene_sets_from_clustering <- 
  clusters_with_descriptions %>% 
  inner_join(read_delim('subset_cluster_names.txt', delim = ',', col_types = cols())) %>% 
  arrange(cluster_number) %>% 
  select(ORF, name, cluster_name) %>% 
  rename('Gene' = name, 'gene_set'  = cluster_name) %>% 
  mutate('set_label' = 'from_clustering')

gene_sets_processes <-
  read_delim('gene_sets_for_gsp1_functions.txt', delim='\t', col_types = cols()) %>% 
  rename('gene_set' = term) %>% 
  mutate('set_label' = 'curated_processes')

gene_sets_complexes <-
  read_delim('all_wodak_complexes.txt', delim='\t', col_types = cols()) %>% 
  rename('Gene' = Name, 'gene_set' = Complex) %>% 
  mutate('set_label' = 'wodak_complexes')

gene_sets <- bind_rows(gene_sets_from_clustering,
                       gene_sets_processes,
                       gene_sets_complexes)

write_delim(gene_sets, 'gene_sets_combined.txt', delim='\t')

gene_sets_min3 <-
  bind_rows(gene_sets_from_clustering, gene_sets_processes, gene_sets_complexes) %>% 
            group_by(gene_set) %>% 
            mutate(count = n()) %>% 
            ungroup() %>% 
            filter(count > 2) %>% 
            select(-count)


write_delim(gene_sets_min3, 'gene_sets_combined_min3.txt', delim='\t')
```

Plot heatmaps, euclidean
```{r, results="hide"}
make_heatmap <- function(mat, Rowv, Colv, main) {
  
  heatmap.2(mat, Rowv = Rowv, Colv = Colv, main = main,
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101), trace='none', density.info="none", keysize = 0.25,
          lmat = rbind(c(4,3,0),c(2,1,0),c(0,0,0)), lhei = c(2, 6, 0.1), lwid = c(1.25, 2, 0.5),
          cexCol = 1, cexRow = 1, srtCol=45)
  
  grid.echo()
  return(grid.grab())
}

gene_set_list <- gene_sets %>% pull(gene_set) %>% unique()
plots_list <- list()

for (i in seq(length(gene_set_list))) {

  genes <-
    read_delim('gene_sets_combined.txt', delim = '\t', col_types = cols()) %>% 
    filter(gene_set == gene_set_list[i]) %>%
    pull(Gene)

  # complete matrices, for plotting comparison dendrograms
  dset.withNA <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols()) %>%
    mutate(mutant = factor(mutant, levels = mut_orderings$seq_order)) %>% 
    gather(key = 'gene', value = score, -mutant) %>%
    filter(gene %in% genes) %>%
    spread(key = gene, value = score)
  mut.mat.withNA <- select(dset.withNA, -mutant) %>% as.matrix()
  rownames(mut.mat.withNA) <- dset.withNA %>% pull(mutant)
  dset_GG.withNA <- dset.withNA %>% filter(mutant %in% mutants_with_GAP_GEF_data)
  mut_GG.mat.withNA <- select(dset_GG.withNA, -mutant) %>% as.matrix()
  rownames(mut_GG.mat.withNA) <- dset_GG.withNA %>% pull(mutant)
  
  # make dataset without NAs for euclidean distance
  dset <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols()) %>% 
    gather(key = 'gene', value = score, -mutant) %>%
    filter(gene %in% genes) %>%
    spread(key = gene, value = score) %>% 
    drop_na() # need to get rid of rows with all NA
  
  mut.mat <- select(dset, -mutant) %>% as.matrix()
  rownames(mut.mat) <- dset %>% pull(mutant)
  mut.dist <- dist(mut.mat, method = "euclidean")
  mut.hc <- hclust(mut.dist, method = "average")
  arr.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
  colnames(arr.mat) <- dset %>% pull(mutant)
  arr.dist <- dist(arr.mat, method = "euclidean")
  arr.hc <- hclust(arr.dist, method = "average")
 
  # GAP GEF dataset
  dset_GG <- dset %>% filter(mutant %in% mutants_with_GAP_GEF_data)
  mut_GG.mat <- select(dset_GG, -mutant) %>% as.matrix()
  rownames(mut_GG.mat) <- dset_GG %>% pull(mutant)
  mut_GG.dist <- dist(mut_GG.mat, method = "euclidean")
  mut_GG.hc <- hclust(mut_GG.dist, method = "average")
  arr_GG.mat <- select(dset_GG, -mutant) %>% as.matrix() %>% t()
  colnames(arr_GG.mat) <- dset_GG %>% pull(mutant)
  arr_GG.dist <- dist(arr_GG.mat, method = "euclidean")
  arr_GG.hc <- hclust(arr_GG.dist, method = "average")

  gl <- list()
  
  gl[[1]] <- make_heatmap(mat = subset(full_emap_arrmat, select=genes), main = 'Full emap',
                          Rowv = as.dendrogram(full_emap_rowtree),
                          Colv = as.dendrogram(arr.hc))
  gl[[2]] <- make_heatmap(mat = mut.mat.withNA, main = 'Seq order',
                          Rowv = FALSE,
                          Colv = as.dendrogram(arr.hc))
  gl[[3]] <- make_heatmap(mat = mut.mat.withNA, main = 'Gene set recluster',
                          Rowv = as.dendrogram(mut.hc),
                          Colv = as.dendrogram(arr.hc))
  gl[[4]] <- make_heatmap(mat = mut.mat.withNA, main = 'Interface',
                          Rowv = as.dendrogram(interface_rowtree),
                          Colv = as.dendrogram(arr.hc))
  gl[[5]] <- grid.text(gene_set_list[i], gp=gpar(fontsize=32))
  gl[[6]] <- make_heatmap(mat = subset(full_emap_GAP_GEF_arrmat, select=genes), main = 'Full emap',
                          Rowv = as.dendrogram(full_emap_GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[7]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'Seq order',
                          Rowv = FALSE,
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[8]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'Gene set recluster',
                          Rowv = as.dendrogram(mut_GG.hc),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[9]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'Interface',
                          Rowv = as.dendrogram(interface_GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[10]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'GAP GEF',
                          Rowv = as.dendrogram(GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))

  grid.arrange(grobs=gl, ncol=5, clip=TRUE, newpage=TRUE)
  plots_list[[i]] <- recordPlot()
  if(i == 2) {break}
}
pdf('images/heatmaps_euclid.pdf', height = 20, width = 30, onefile = TRUE)
for (my.plot in plots_list) {
  replayPlot(my.plot)
}
graphics.off()

```


Plot heatmaps, correlation
```{r}
make_heatmap <- function(mat, Rowv, Colv, main) {
  
  heatmap.2(mat, Rowv = Rowv, Colv = Colv, main = main,
          col = colorRampPalette(c('blue','black','yellow')),
          breaks = seq(-3, 3, length.out = 101), trace='none', density.info="none", keysize = 0.25,
          lmat = rbind(c(4,3,0),c(2,1,0),c(0,0,0)), lhei = c(2, 6, 0.1), lwid = c(1.25, 2, 0.5),
          cexCol = 1, cexRow = 1, srtCol=45)
  grid.echo()
  return(grid.grab())
}

gene_set_list <- gene_sets_min3 %>% filter(set_label != 'wodak_complexes') %>% pull(gene_set) %>% unique()
# gene_set_list <- gene_sets_min3 %>% pull(gene_set) %>% unique()
plots_list <- list()

for (i in seq(31, length(gene_set_list))) {
  
  genes <-
    read_delim('gene_sets_combined_min3.txt', delim = '\t', col_types = cols()) %>% 
    filter(gene_set == gene_set_list[i]) %>%
    pull(Gene)
    
  # complete matrices, for plotting comparison dendrograms
  dset.withNA <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols()) %>%
    mutate(mutant = factor(mutant, levels = mut_orderings$seq_order)) %>% 
    gather(key = 'gene', value = score, -mutant) %>%
    filter(gene %in% genes) %>%
    spread(key = gene, value = score)
    
  mut.mat.withNA <- select(dset.withNA, -mutant) %>% as.matrix()
  rownames(mut.mat.withNA) <- dset.withNA %>% pull(mutant)
  dset_GG.withNA <- dset.withNA %>% filter(mutant %in% mutants_with_GAP_GEF_data)
  mut_GG.mat.withNA <- select(dset_GG.withNA, -mutant) %>% as.matrix()
  rownames(mut_GG.mat.withNA) <- dset_GG.withNA %>% pull(mutant)
  
  # make dataset without NAs for euclidean distance
  dset <- read_delim('datasets/gsp1_emap_for_clustering.txt', delim = '\t', col_types = cols()) %>% 
    gather(key = 'gene', value = score, -mutant) %>%
    filter(gene %in% genes) %>%
    spread(key = gene, value = score) %>% 
    mutate(count_non_na = rowSums(!is.na(.))-1) %>% 
    filter(count_non_na >=3) %>%  # need at least 3 points for a correlation
    select(-count_non_na)
  if(nrow(dset) < 3) next # need at least 3 rows to show heatmap
  
  mut.mat <- select(dset, -mutant) %>% as.matrix() %>% t()
  colnames(mut.mat) <- dset %>% pull(mutant)
  mut.hc <- clustfn(mut.mat)

  arr.mat <- select(dset, -mutant) %>% as.matrix()
  rownames(arr.mat) <- dset %>% pull(mutant)
  arr.hc <- clustfn(arr.mat)

  # GAP GEF dataset
  dset_GG <- dset %>% filter(mutant %in% mutants_with_GAP_GEF_data)
  mut_GG.mat <- select(dset_GG, -mutant) %>% as.matrix() %>% t()
  colnames(mut_GG.mat) <- dset_GG %>% pull(mutant)
  mut_GG.hc <- clustfn(mut_GG.mat)
  arr_GG.mat <- select(dset_GG, -mutant) %>% as.matrix()
  rownames(arr_GG.mat) <- dset_GG %>% pull(mutant)
  arr_GG.hc <- clustfn(arr_GG.mat)
  
  
  gl <- list()

  gl[[1]] <- make_heatmap(mat = subset(full_emap_arrmat, select=colnames(arr.mat)), main = 'Full emap',
                          Rowv = as.dendrogram(full_emap_rowtree),
                          Colv = as.dendrogram(arr.hc))
  gl[[2]] <- make_heatmap(mat = mut.mat.withNA, main = 'Seq order',
                          Rowv = FALSE,
                          Colv = as.dendrogram(arr.hc))
  gl[[3]] <- make_heatmap(mat = arr.mat, main = 'Gene set recluster',
                          Rowv = as.dendrogram(mut.hc),
                          Colv = as.dendrogram(arr.hc))
  gl[[4]] <- make_heatmap(mat = mut.mat.withNA, main = 'Interface',
                          Rowv = as.dendrogram(interface_rowtree),
                          Colv = as.dendrogram(arr.hc))
  gl[[5]] <- grid.text(gene_set_list[i], gp=gpar(fontsize=32))
  gl[[6]] <- make_heatmap(mat = subset(full_emap_GAP_GEF_arrmat, select=colnames(arr_GG.mat)), main = 'Full emap',
                          Rowv = as.dendrogram(full_emap_GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[7]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'Seq order',
                          Rowv = FALSE,
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[8]] <- make_heatmap(mat = arr_GG.mat, main = 'Gene set recluster',
                          Rowv = as.dendrogram(mut_GG.hc),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[9]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'Interface',
                          Rowv = as.dendrogram(interface_GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))
  gl[[10]] <- make_heatmap(mat = mut_GG.mat.withNA, main = 'GAP GEF',
                          Rowv = as.dendrogram(GAP_GEF_rowtree),
                          Colv = as.dendrogram(arr_GG.hc))

  grid.arrange(grobs=gl, ncol=5, clip=TRUE, newpage=TRUE)
  plots_list[[length(plots_list)+1]] <- recordPlot()
  
}
pdf('images/heatmaps_corr_second.pdf', height = 20, width = 30, onefile = TRUE)
for (my.plot in plots_list) {
  replayPlot(my.plot)
}

graphics.off()
```

